Fast and scalable Gaussian process modeling of stellar variability \vspace{-3\baselineskip}

### 2016-09-04 paper/ms.tex
Moved figure; updated ms.tex

Rather than using $\beta$ and its complex conjugate as components of the kernel, we instead
find the real and imaginary components of the complex equationi for $\beta$, and 
discard the $\beta^*$ equation, which is redundant.  This gives four additional equations for
each $\beta_j$ with non-zero imaginary component, while the kernel components with real
$\beta_j$ still only have two additional components in the extended matrix.  We will enumerate
the number of real $\beta$'s as $p_0$, while the total number of $\beta$'s is still $p$.
This gives a total number of equations to be solved with the extended matrix of $N_{ex}= 
(4(p-p_0)+2p_0+1)\times(N-1)+1$, where $n$ is the number of data points.

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[scale=0.175]{./twoterm.eps}
\hspace{0.2in}
\includegraphics[scale=1.0]{./images/colorcode.eps}
\end{center}
\caption{Pictorial description of the extended sparse matrix where $N=10$, $p_0=0$, and $p=2$, following
the example shown in \citet{Ambikasaran2015}.}
\label{matrix_structure}
\end{figure}

>>>>

Rather than using $\beta$ and its complex conjugate as components of the kernel, we instead
find the real and imaginary components of the complex equation for $\beta$ by taking the
sum and difference of the $\beta$ and $\beta^*$ equations (divided by 2 and $2i$, respectively), 
and then discard the $\beta^*$ equation, which is redundant.  This keeps the same number of
additional equations for each $\beta_j$ with non-zero imaginary component (four additional
equations in the extended matrix), but converts the complex equations to real, thus avoiding
complex arithmetic, while the kernel components with real $\beta_j$ still only have two 
additional components in the extended matrix.  The extended matrix adds an extra band above
and below the diagonal when the $\beta$ and $\beta^*$ equations are combined since this
mixes the components of the original equations which are shifted by one column from one
another.  We will enumerate the number of real $\beta$'s as $p_0$, while the total number 
of $\beta$'s is still $p$.  This gives a total number of equations to be solved with the 
extended matrix of $N_{ex}= (4(p-p_0)+2p_0+1)\times(N-1)+1$, where $n$ is the number of data 
points.

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[scale=0.175]{./twoterm.eps}
\hspace{0.2in}
\includegraphics[scale=1.0]{./colorcode.eps}
\end{center}
\caption{Pictorial description of the extended sparse matrix where $N=10$, $p_0=0$, and $p=2$, following
the example shown in \citet{Ambikasaran2015}.}
\label{matrix_structure}
\end{figure}
